Repeatability Test

### 2017-09-24 pt_characterization/rep_check/res1.tex
PT draft modified

\subsection{PT}

@@

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT 
exhibited in Section~\ref{sec:first_run}. 
Note that the histograms from the task lengths of 8192 and 16384 seconds 
to be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}. 
are brought into Figure~\ref{fig:hist3d} for completeness. The x-, y-, z-axes 
indicate the normalized PT ranging from 0 to 100, task length in log scale, 
and relative frequency of each histogram, such that for each INC 
it is scaled from 0 (the shortest) to 100 (the highest).

@@

\pagebreak
\clearpage
Figure~\ref{fig:hist3d_u} represents a 3D plot of collecting the histograms of user time only
exhibited in Section~\ref{sec:first_run}. 
\begin{figure}[htp!]
%\vspace{-.3in}
	\centering
	\includegraphics[scale=1]{u_s_time/3dplot_utime_only}\label{fig:3d_plot_u}
	\caption{3D histograms on INC: u time only~\label{fig:hist3d_u}}
\end{figure}

>>>>

\subsection{PT~\label{sec:1st_pt}}

@@

\paragraph{Stacked Histograms in a 3D Plot:}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting the histograms of PT 
exhibited in Section~\ref{sec:1st_pt}. 
Note that the histograms from the task lengths of 8192 and 16384 seconds 
to be shown in Figures~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}. 
are brought into Figure~\ref{fig:hist3d} for completeness. The x-, y-, z-axes 
indicate the normalized PT ranging from 0 to 100, task length in log scale, 
and relative frequency of each histogram, such that for each INC 
it is scaled from 0 (the shortest) to 100 (the highest).

@@

\pagebreak
\clearpage
Figure~\ref{fig:hist3d_u} represents a 3D plot of collecting the histograms of user time only
exhibited in Section~\ref{sec:first_run}. 
\begin{figure}[htp!]
%\vspace{-.3in}
	\centering
	\includegraphics[scale=1]{u_s_time/3dplot_utime_only}\label{fig:3d_plot_u}
	\caption{3D histograms on INC: user time only~\label{fig:hist3d_u}}
\end{figure}
